Test

### 2016-07-22 Berkeley_PD_Stop.Rmd
072216

#read data
stop_df <- read.csv("~/Desktop/Berkeley_PD_-_Stop_Data.csv")

# Delete meaningless information and fix typos
stop_df <- stop_df %>%
  mutate(Dispositions = as.character(stop_df$Dispositions)) %>%
  mutate(Dispositions = str_replace(Dispositions, "zz do not use Assist", "")) %>%
  mutate(Dispositions = str_replace(Dispositions, "FA - TIGHT, ", "")) %>%
  mutate(Dispositions = str_replace(Dispositions, "[0]{6}[1]?", "00000"))

# Split people information and other information
stop_df <- stop_df %>%
  mutate(Other = str_replace_all(Dispositions, "[ ,]{0,2}[a-zA-Z0-9]{6}", "")) %>%
  mutate(Other = str_replace_all(Other, "^[ ,]{0,4}", "")) %>%
  mutate(Other = str_replace(Other, ",$", ""))

# Delete Other information from Disposition
OtherInformation <- c( "^M$" = "", ", M$" = "", "M, P$" = "", "P[, ]{0,2}" = "", "AR[, ]{0,2}" = "", "IN[, ]{0,2}" = "", "FC[, ]{0,2}" = "", "CO[, ]{0,2}" = "", "MH[, ]{0,2}" = "", "TOW[, ]{0,2}" = "", "0[, ]{0,2}" = "", "00000[, ]{0,2}" = "")
stop_df <- stop_df %>%
  mutate(Dispositions = str_replace_all(Dispositions, OtherInformation)) %>%
  mutate(Dispositions = str_replace_all(Dispositions, "[, ]{0,2}$", ""))

View(stop_df)

#mutate dispositions column to only contain six character cases

View(stop_df)
View(dispositions)
###

>>>>

stop_df <- read.csv("~/Desktop/Berkeley_PD_-_Stop_Data.csv")

#disps <- as.character(stop_df$Dispositions)
#max(nchar(disps))
#disps[which(nchar(disps) == 42)]

stop_df <- mutate(stop_df, Dispositions = as.character(stop_df$Dispositions))

#entries with "zz do not use Assist" 
stop_df <- mutate(stop_df, Dispositions = str_replace_all(stop_df$Dispositions, "zz do not use Assist", ""))
#entries with "FA - TIGHT"
stop_df <- mutate(stop_df, Dispositions = str_replace_all(stop_df$Dispositions, "FA - TIGHT", ""))
#fixing entries that were input incorrectly
stop_df <- mutate(stop_df, Dispositions = str_replace_all(stop_df$Dispositions, "[0]{6}[1]?", "00000"))

#deal with special cases first 
stop_df <- mutate(stop_df, Other = str_replace_all(stop_df$Dispositions, "[ ,]{0,2}[a-zA-Z0-9]{6}", ""))
stop_df <- mutate(stop_df, Other = str_replace_all(stop_df$Other, "^[ ,]{0,4}", ""))

#mutate dispositions column to only contain six character cases
stop_df <- mutate(stop_df, Dispositions = str_match_all(stop_df$Dispositions, "[a-zA-Z0-9]{6}"))

dispositions <- separate(stop_df, Dispositions, into = c("Empty", "Individual_1", "Individual_2", "Individual_3", "Individual_4", "Individual_5"), extra = "merge", fill = "right")

View(stop_df)
View(dispositions)

###IGNORE EVERYTHING AFTER THIS
